{\it E}nKCF: Ensemble of Kernelized Correlation Filters for High-Speed, Object Tracking

### 2017-06-21 bmvc_review.tex
Revised the experimental section.

Table \ref{table:Comparison_to_LCT} presents the performance of
different combinations of the proposed algorithm. In short, we
empirically verified that \textit{E}nKCF is an optimal combination in
terms of tracking accuracy and run-time performance. We could achieve
4.26\% higher in accuracy by running $R_{R}^{t}$ and $R_{S}$ at every
frame, but this combination wills sacrifice run-time performance 317
fps.  To be more specific, we employ $R_{s}$ and $R_{t}^{L}$ or
$R_{t}^{S}$ to run them in every frame in a similar way to the
multiple correlation filter framework of the LCT tracker
\cite{ma2015long}. Running another filter, $R_{t}^{L}$ or $R_{t}^{S}$,
in the {\it E}nKCF framework not only boosts run-time performance but
also increases accuracy. Lastly, we run $R_{L}$, $R_{t}^{S}$ and
$R_{s}$ in every frame.  $R_{t}^{S}$ uses the translation estimated by
$R_{t}^{L}$ to update translation and $R_{s}$ uses the final
translation estimation given by $R_{t}^{S}$ to update the
scale. Interestingly, running two complementary translation filter
results in significant improvement at the cost of decreased run-time
performance. In summary, running two (complementary) translation
filters and a scale filter as {\it E}nKCF not only increases run-time
performance but also offers more accurate tracker than the baseline
method with one translation and one scale filter.
\begin{table}[!h]
\smaller
\begin{center}
\color{green}--- Best \hspace{.15\linewidth}\color{red}--- $2^{nd}$ Best \hspace{.15\linewidth}\color{blue}--- $3^{th}$ Best \color{black}\\
\resizebox{\textwidth}{!}{\begin{tabular}{|l|c|c|c|c|c|c|c|c|c|}
\hline
Method & {\it E}nKCF & $R_{t}^{S}$+$R_{t}^{L}$+$R_{s}$ & $R_{t}^{L}$+$R_{s}$ & $R_{t}^{S}$+$R_{s}$ & $R_{t}^{L}$* & $R_{t}^{S}$* & $R_{t}^{L}$+$R_{s}$* & $R_{t}^{S}$+$R_{s}$* & $R_{t}^{L}+R_{t}^{S}$+$R_{s}$* \\
\hline\hline
Pr. ($20$px) & \color{blue}53.9 & 48.93 &52.41 & 48.10 & 51.88 & 51.29 & \color{red} 55.85 & 52.14 & \color{green}58.16 \\
SR ($50\%$) & \color{red} 40.2 & 36.75 & 38.23 & 36.04 & 35.12 & 34.43 & \color{blue}39.89 & 38.51 & \color{green}41.58 \\
FPS & \color{red} 416 & \color{blue}412 & 370 & \color{green}425 & 365 & 384 & 135 & 151 & 99 \\
\hline
\end{tabular}}
\end{center}
\caption{Evaluations on different combinations of the KCFs for UAV123
  dataset. We removed the particle filter from this experiment. The
  $2^{nd}$ method fliped the way of deploying $R_{t}^{L}$ and
  $R_{t}^{S}$ (fig.~\ref{Workflows}). The $3^{th}$ method removed
  $R_{t}^{S}$ and replaces with $R_{t}^{L}$ whereas the $4^{th}$ one
  removes $R_{t}^{L}$. {\it Burak: $3^{th}$ and $3^{th}$?} {\it YoungWoo : I meant to say $4^{th}$} The methods
  marked with "*" run the filters on every frame in the listed
  order. The LCT tracker \cite{ma2015long} runs a translation and
  scale filter in every frame (similar to the methods at the $7^{th}$ and $8^{th}$
  columns) {\it Burak: Not in $7^{th}$?} {\it YoungWoo: I meant to say $7^{th}$ and $8^{th}$} and couples a re-detection
  method to perform long-term tracking at $\approx30$ fps.}
\label{table:Comparison_to_LCT}
\end{table}

For the $UAV123$ dataset, we also evaluated the performance of the
{\it E}nKCF with and without the particle filter. In particular, we
use 50 sequences labeled as no abrupt camera motion in the dataset. To
evaluate the robustness of particle filter, we add noise, drawn from a
uniform distribution ($[-20,20]$), to the translation estimations of
the KCFs. In these settings, the {\it E}nKCF with particle filter
achieves $51.98\%$ precision ($20$px), outperforming the baseline {\it
  E}nKCF by $6.32\%$. {\it Burak: the baseline here is the one without
  particle filter?} {\it YoungWoo : Yes, the baseline is the one without Particle Filter.} 
In summary, with the removal of global camera
motion, the integration of particle filter into the {\it E}nKCF as
shown in fig.~\ref{Workflows} further improved the results.

>>>>

\textbf{Finding Optimal Combination and Deployment Order of Multiple
  KCFs} In addition to the comparison with other tracking methods, we
also conducted an experiment to see what combination and deployment
order of the KCF work best. Table \ref{table:Comparison_to_LCT}
presents results of this experiment. For this experiment, we removed
the particle filter. The method at the $2^{nd}$ column fliped the
order of deploying $R_{t}^{L}$ and $R_{t}^{S}$ as presented at Figure
\ref{Workflows}. The one at the $3^{th}$ column removed $R_{t}^{S}$
and replaces with $R_{t}^{L}$ whereas the one at the $4^{th}$ column
removes $R_{t}^{L}$. The methods marked with ``*'' ran the filters on
every frame in the listed order. The methods at the $7^{th}$ and
$8^{th}$ columns ran a translation and a scale filter on every frame
which is very similar to the way the LCT tracker \cite{ma2015long}
runs. To be precise, the LCT tracker comes with a re-detection method
for a long-term tracking. In short, we empirically verified that
\textit{E}nKCF is an optimal way of using multiple KCFs, in terms of
tracking accuracy and run-time performance. For example, we could
achieve 4.26\% higher in accuracy by running $R_{R}^{t}$ and $R_{S}$
at every frame, but this combination wills sacrifice run-time
performance, slowing down 317 fps. Lastly, we run $R_{L}$, $R_{t}^{S}$
and $R_{s}$ in every frame where $R_{t}^{S}$ uses the translation
estimated by $R_{t}^{L}$ to update translation and $R_{s}$ uses the
final translation estimation given by $R_{t}^{S}$ to update the scale.
\begin{table}[!h]
\smaller
\begin{center}
\color{green}--- Best \hspace{.15\linewidth}\color{red}--- $2^{nd}$ Best \hspace{.15\linewidth}\color{blue}--- $3^{th}$ Best \color{black}\\
\resizebox{\textwidth}{!}{\begin{tabular}{|l|c|c|c|c|c|c|c|c|c|}
\hline
Method & {\it E}nKCF & $R_{t}^{S}$+$R_{t}^{L}$+$R_{s}$ & $R_{t}^{L}$+$R_{s}$ & $R_{t}^{S}$+$R_{s}$ & $R_{t}^{L}$* & $R_{t}^{S}$* & $R_{t}^{L}$+$R_{s}$* & $R_{t}^{S}$+$R_{s}$* & $R_{t}^{L}+R_{t}^{S}$+$R_{s}$* \\
\hline\hline
Pr. ($20$px) & \color{blue}53.9 & 48.93 &52.41 & 48.10 & 51.88 & 51.29 & \color{red} 55.85 & 52.14 & \color{green}58.16 \\
SR ($50\%$) & \color{red} 40.2 & 36.75 & 38.23 & 36.04 & 35.12 & 34.43 & \color{blue}39.89 & 38.51 & \color{green}41.58 \\
FPS & \color{red} 416 & \color{blue}412 & 370 & \color{green}425 & 365 & 384 & 135 & 151 & 99 \\
\hline
\end{tabular}}
\end{center}
\caption{Results of running different combinations of the KCFs for
  UAV123 dataset. This table empirically supported the usefulness of
  combining multiple KCFs as long as the deployment order is optimal.}
\label{table:Comparison_to_LCT}
\end{table}

For the $UAV123$ dataset, we also evaluated the performance of the
{\it E}nKCF with and without the particle filter. In particular, we
use 50 sequences labeled as no abrupt camera motion in the dataset. To
evaluate the robustness of particle filter, we add noise, drawn from a
uniform distribution ($[-20,20]$), to the translation estimations of
the KCFs. In these setup, the {\it E}nKCF with particle filter
achieves $51.98\%$ precision ($20$px), outperforming the one without
particle filter {\it E}nKCF by $6.32\%$. Thus, with the removal of
global camera motion, the integration of particle filter into the {\it
  E}nKCF as shown in Figure \ref{Workflows} further improved the
results.
